The regularity of ODEs and thimble integrals \\ with respect to Borel summation \begin{draft}\textbf{[DRAFT]}\end{draft}

### 2024-10-11 borel-regularity.tex
Write out new proposed convolution statement
Sketch new definition of convolution

The function $\phi \ast_{\zeta, \alpha} \psi$ is holomorphic, as long as it is well-defined. \begin{todo}[Is it clear the convolution is holomorphic?]\end{todo} On a domain $\Omega_\alpha$ which is star-shaped around $\zeta = \alpha$, the convolution product $\ast_{\zeta, \alpha}$ induces a $\C$-algebra structure on $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$. The Laplace transform $\laplace_{\zeta_\alpha, 0}$ is special, because it is an algebra isomorphism with respect to $\ast_{\zeta_\alpha, 0}$.
\begin{prop}\label{prop:convolution_iso_laplace}
\begin{todo}[Replace $\zeta_\alpha$ with $\zeta$ throughout statement and proof, unless there's some obstacle.]\end{todo} Let $\phi,\psi$ be two holomorphic functions on $B$ whose Laplace transform $\laplace_{\zeta_\alpha,0}$ is well defined. Then
\begin{equation*}
\laplace_{\zeta_\alpha,0}[\phi\ast_{\zeta_\alpha,0}\psi]=\laplace_{\zeta_\alpha,0}[\phi]\,\laplace_{\zeta_\alpha,0}[\psi]\,.
\end{equation*}

@@

Note that if $\phi$ and $\psi$ have integrable singularities at $\zeta_\alpha = 0$, the product $\phi(a)\,\psi(a')$ has both singularities, but in different positions---one at $s = 0$, and the other at $s = 1$. This guarantees that $\phi(a)\,\psi(a')$ is integrable over the interval $s \in [0, 1]$.\end{revised}

@@

@@

@@

The convolution and Laplace integrals can be combined into an integral over a real two-dimensional wedge $\mathcal{N}$ within the complex three-dimensional space $B^3$:
\[ \laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}] = \int_\mathcal{M} e^{-z\zeta}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta\,. \]
The coordinates $\zeta(a)$, $\zeta(a')$, $\zeta$ parameterize $B^3$, and the real wedge $\mathcal{N}$ lies within the complex surface cut out by the equation equation $\zeta(a) + \zeta(a') = \zeta$. Thus, on $\mathcal{N}$, we have the identity
\begin{align*}
d\zeta(a) + d\zeta(a') & = d\zeta \\
d\zeta(a) \wedge \big[d\zeta(a) + d\zeta(a')\big] & = d\zeta(a) \wedge d\zeta \\
d\zeta(a) \wedge d\zeta(a') & = d\zeta(a) \wedge d\zeta\,,
\end{align*}
which we can substitute into the integral above to get
\begin{align*}
\laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}] & = \int_\mathcal{M} e^{-z[\zeta(a) + \zeta(a')]}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta(a') \\
& = \int_\mathcal{M} \left[ e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \right] \wedge \left[ e^{z\zeta(a')}\,\psi(a')\,d\zeta(a') \right]\,.
\end{align*}
\begin{todo}Now we need to explain why the grid lines can be projected to $\mathcal{J}_{\zeta(a), \alpha}$ and $\mathcal{J}_{\zeta(a'), \beta}$. Something seems off here. The tip of the wedge $\mathcal{N}$ should be at $\zeta = \alpha + \beta$, since that's the beginning of the ray $\mathcal{J}_{\zeta, \alpha + \beta}$. At that point, though, according to our definitions, $\mathcal{S}(\zeta)$ should consist of the point $\zeta(a) = \alpha + \beta$, and $\mathcal{S}'(\zeta)$ should consist of the point $\zeta(a') = 0$.

@@

Maybe me actually need to change the statement? I think the argument might wrap up neatly if the convolution on the left-hand side were $\phi \ast_{\zeta_\alpha, \beta} \psi$ instead.
\end{todo}
\begin{align*}
\laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}] & = \int_{?} e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \int_{?} e^{z\zeta(a')}\,\psi(a')\,d\zeta(a')
\end{align*}
\end{draft}

@@

In our treatmeant, we will restrict the Borel transform to the space of $1$-Gevrey series and the Laplace transform to $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ with $\sigma>-1$ and $\Lambda>0$, for some domain $\Omega_\alpha$ as in Figure~\ref{fig:sectorial_domain-pos-fre}.
\begin{definition}
For $\nu \in (-\infty, 1)$, the \textit{fractional integral} $\partial^{\nu-1}_{\zeta, \alpha}$ is defined by
%
%%\[ [\partial^{\nu-1}_{\zeta, \alpha} \phi](a) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta=\alpha}^a \big(\zeta(a)-\zeta\big)^{-\nu} \phi \,d\zeta\,. \] 
\[ \partial^{\nu-1}_{\zeta, \alpha} \phi \defeq \frac{1}{\Gamma(1-\nu)} \int_{\mathcal{S}(\zeta)} \big(\zeta-\zeta(a)\big)^{-\nu} \phi(a) \,d\zeta(a)\,, \]
where $\mathcal{S}(\zeta)$ is the line segment from $\zeta(a)=\alpha$ to $\zeta(a)=\zeta$.

>>>>

\color{Turquoise}
Let $\phi\in\singexpalg{\sigma}(\Omega_\alpha),\psi\in\singexpalg{\sigma'}(\Omega_\beta)$ . Choose a translation coordinate $\zeta$ on $B$ and a base point $\zeta = \gamma$. The convolution product $\phi\ast_{\zeta,\gamma}\psi$ is the function on $B$ defined by the integral
\phi \ast_{\zeta, \gamma} \psi \defeq \int_{\substack{\mathcal{S}(\zeta_\alpha)\times\mathcal{S}'(\zeta_\beta)\\ \zeta_\alpha(a)+\zeta_\beta(a')=\zeta}} \phi(a)\,\psi(a')\,d\zeta(a),
where $\mathcal{S}(\zeta_\alpha)$ is the line segment from $\zeta_\alpha(a)=\gamma$ to $\zeta_\alpha(a)=\zeta$, and $\mathcal{S}'(\zeta_\beta)$ is the line segment from $\zeta_\beta(a')=\zeta-\gamma$ to $\zeta_\beta(a')=0$.
Take $\phi\in\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ and $\psi\in\singexp{\sigma'}{\Lambda'}(\Omega_\beta)$, with $\sigma,\sigma'\in (-1,\infty)$. The convolution $\phi\ast_{\zeta,\alpha+\beta}\psi$ belongs to $\singexp{\sigma''}{\Lambda''}(\Omega_{\alpha+\beta})$, where $\Lambda'' = \Lambda + \Lambda'$ and $\sigma'' = 1 + \sigma + \sigma'$.  \end{lemma}    
\left|\phi\ast_{\zeta,\alpha}\psi\right|&\le\int_{\substack{\mathcal{S}(\zeta)\times\mathcal{S}'(\zeta)\\ \zeta(a)+\zeta(a')=\zeta}} |\phi(a)|\,|\psi(a')|\,|d\zeta(a)| \\
& = \int_{\substack{\mathcal{S}(\zeta_\alpha)\times\mathcal{S}'(\zeta)\\ \zeta_\alpha(a)+\zeta(a')=\zeta_\alpha}} |\phi(a)|\,|\psi(a')|\,|d\zeta_\alpha(a)|\,,
where $\mathcal{S}(\zeta_\alpha)$ is the line segment from $\zeta_\alpha(a)=0$ to $\zeta_\alpha(a)=\zeta_\alpha$, and $\mathcal{S}'(\zeta)$ is the line segment from $\zeta(a')=\zeta_\alpha$ to $\zeta(a')=0$. We introduce the variable $s\in[0,1]$ such that $\zeta_\alpha(a)=s\zeta_\alpha$ and $\zeta_\alpha(a')=(1-s)\zeta_\alpha$:
  \int_{\substack{\mathcal{S}(\zeta_\alpha)\times\mathcal{S}'(\zeta)\\ \zeta_\alpha(a)+\zeta(a')=\zeta_\alpha}} |\phi(a)|\,|\psi(a')|\,|d\zeta_\alpha(a)|&= |\zeta_\alpha|\int_0^1 |\phi(a)|\,|\psi(a')|\, ds\,.
Since $\phi$ and $\psi$ have bounded norms,
|\zeta_\alpha|\int_0^1 |\phi(a)|\,|\psi(a')|\, ds&\le \|\phi\|_{\sigma,\Lambda} \|\psi\|_{\sigma',\Lambda'} |\zeta_\alpha|^{1+\sigma+\sigma'}\int_0^1  |s|^{\sigma}e^{\Lambda s |\zeta_\alpha|}\,|1-s|^{\sigma'}e^{\Lambda' (1-s)|\zeta_\alpha|}\,ds\\
&\lesssim |\zeta_\alpha| ^{1+\sigma+\sigma'} e^{(\Lambda+\Lambda')|\zeta_\alpha|}\int_0^1  s^{\sigma}\,(1-s)^{\sigma'}\,ds\\
&=\lesssim |\zeta_\alpha| ^{1+\sigma+\sigma'} e^{(\Lambda+\Lambda')|\zeta_\alpha|}\,.
\begin{old}
The function $\phi \ast_{\zeta, \alpha} \psi$ is holomorphic, as long as it is well-defined.\end{old}

On a domain $\Omega_\alpha$ which is star-shaped around $\zeta = \alpha$, the convolution product $\ast_{\zeta, \alpha}$ induces a $\C$-algebra structure on $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$. The Laplace transform $\laplace_{\zeta_\alpha, 0}$ is special, because it is an algebra isomorphism with respect to $\ast_{\zeta_\alpha, 0}$.
\begin{prop}\label{prop:convolution_iso_laplace}
\begin{todo}[Replace $\zeta_\alpha$ with $\zeta$ throughout statement and proof, unless there's some obstacle.]\end{todo} \begin{revised}For any two functions $\phi \in \singexpalg{\sigma}(\Omega)$ and $\psi \in \singexpalg{\sigma'}(\Omega)$, with $\sigma, \sigma' \in (-1, \infty)$, we have\end{revised} \begin{old}Let $\phi,\psi$ be two holomorphic functions on $B$ whose Laplace transform $\laplace_{\zeta_\alpha,0}$ is well defined. Then\end{old}
\begin{equation}\label{eqn:laplace-convol1}
\laplace_{\zeta,0}[\phi\ast_{\zeta,0}\psi]=\laplace_{\zeta,0}[\phi]\,\laplace_{\zeta,0}[\psi]\,.
\end{equation}
\begin{todo}
Add assumption that the Laplace transform of the convolution is well defined. I think we could simply assume $\phi,\psi$ being of exponential type.    
\end{todo}
\end{prop}
\begin{proof}
\begin{revised}
The left-hand side of equation~\eqref{eqn:laplace-convol1} expands to
\[ \laplace_{\zeta,0}[{\phi}\ast_{\zeta, 0}{\psi}] = \int_{\mathcal{J}_{\zeta, 0}} d\zeta\,e^{-z\zeta}\int_{\substack{\mathcal{S}(\zeta) \times \mathcal{S}'(\zeta) \\ \zeta(a) + \zeta(a') = \zeta}}  \phi(a)\,\psi(a')\, d\zeta(a)\,. \]
In the convolution integral, $a$ follows the straight path $\mathcal{S}(\zeta)$ where $\zeta(a)$ runs from $0$ to $\zeta$, while $a'$ follows the straight path $\mathcal{S}'(\zeta)$ where $\zeta(a')$ runs from $\zeta$ to $0$.

The convolution and Laplace integrals can be combined into an integral over a real two-dimensional wedge $\mathcal{N}$ within the complex three-dimensional space $B^3$:
\[ \laplace_{\zeta,0}[{\phi}\ast_{\zeta, 0}{\psi}] = \int_\mathcal{N} e^{-z\zeta}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta\,. \]
The coordinates $\zeta(a)$, $\zeta(a')$, $\zeta$ parameterize $B^3$, and the real wedge $\mathcal{N}$ lies within the complex surface cut out by the equation equation $\zeta(a) + \zeta(a') = \zeta$. Thus, on $\mathcal{N}$, we have the identity
\begin{align*}
d\zeta(a) + d\zeta(a') & = d\zeta \\
d\zeta(a) \wedge \big[d\zeta(a) + d\zeta(a')\big] & = d\zeta(a) \wedge d\zeta\\
d\zeta(a) \wedge d\zeta(a') & = d\zeta(a) \wedge d\zeta\,,
\end{align*}
which we can substitute into the integral above to get
\begin{align*}
\laplace_{\zeta,0}[{\phi}\ast_{\zeta,0}{\psi}] & = \int_\mathcal{N} e^{-z[\zeta(a) + \zeta(a')]}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta(a') \\
& = \int_\mathcal{N} \left[ e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \right] \wedge \left[ e^{-z\zeta(a')}\,\psi(a')\,d\zeta(a') \right]\,.
\end{align*}

By construction, the range of $\zeta$ on $\mathcal{N}$ is $[0, \infty)$. From the definitions of the paths $\mathcal{S}(\zeta)$ and $\mathcal{S}'(\zeta)$, it follows that the ranges of $\zeta(a)$ and $\zeta(a')$ on $\mathcal{N}$ are also both $[0, \infty)$. In fact, projection onto the $a$ and $a'$ factors of $B^3$ identifies $\mathcal{N}$ with $\mathcal{J}_{\zeta(a), 0} \times \mathcal{J}_{\zeta(a'), 0} \subset B^2$. We can therefore factorize the integral above using Fubini's theorem, yielding the desired identity:
\laplace_{\zeta,0}[{\phi}\ast_{\zeta,0}{\psi}] & = \left[ \int_{\mathcal{J}_{\zeta(a), 0}} e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \right] \left[ \int_{\mathcal{J}_{\zeta(a'), 0}} e^{-z\zeta(a')}\,\psi(a')\,d\zeta(a') \right]\,.
\begin{old}

@@

Note that if $\phi$ and $\psi$ have integrable singularities at $\zeta_\alpha = 0$, the product $\phi(a)\,\psi(a')$ has both singularities, but in different positions---one at $s = 0$, and the other at $s = 1$. This guarantees that $\phi(a)\,\psi(a')$ is integrable over the interval $s \in [0, 1]$.

@@

\end{old}

@@

\[ \laplace_{\zeta,\alpha+\beta}[\phi \ast_{\zeta_\alpha, \beta} \psi] = \int_{\mathcal{J}_{\zeta, \alpha+\beta}} d\zeta\,e^{-z\zeta}\int_{\substack{\mathcal{S}(\zeta_\alpha) \times \mathcal{S}'(\zeta_\alpha) \\ \zeta_\alpha(a) + \zeta_\alpha(a') = \zeta_\alpha}}  \phi(a)\,\psi(a')\, d\zeta_\alpha(a)\,. \]
In the convolution integral, $a$ follows the straight path $\mathcal{S}(\zeta_\alpha)$ where $\zeta_\alpha(a)$ runs from $\beta$ to $\zeta_\alpha$, while $a'$ follows the straight path $\mathcal{S}'(\zeta_\alpha)$ where $\zeta_\alpha(a')$ runs from $\zeta_\alpha - \beta$ to $0$.

@@

The convolution and Laplace integrals can be combined into an integral over a real two-dimensional wedge $\mathcal{N}$ within the complex three-dimensional space $B^3$:
\[ \laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}] = \int_\mathcal{N} e^{-z\zeta}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta\,. \]
The coordinates $\zeta(a)$, $\zeta(a')$, $\zeta$ parameterize $B^3$, and the real wedge $\mathcal{N}$ lies within the complex surface cut out by the equation equation $\zeta(a) + \zeta(a') = \zeta$. Thus, on $\mathcal{N}$, we have the identity
\begin{align*}
d\zeta(a) + d\zeta(a') & = d\zeta \\
d\zeta(a) \wedge \big[d\zeta(a) + d\zeta(a')\big] & = d\zeta(a) \wedge d\zeta \\
d\zeta(a) \wedge d\zeta(a') & = d\zeta(a) \wedge d\zeta\,,
\end{align*}
which we can substitute into the integral above to get
\begin{align*}
\laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}] & = \int_\mathcal{N} e^{-z[\zeta(a) + \zeta(a')]}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta(a') \\
& = \int_\mathcal{N} \left[ e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \right] \wedge \left[ e^{z\zeta(a')}\,\psi(a')\,d\zeta(a') \right]\,.
\end{align*}
\begin{todo}Now we need to explain why the grid lines can be projected to $\mathcal{J}_{\zeta(a), \alpha}$ and $\mathcal{J}_{\zeta(a'), \beta}$. Something seems off here. The tip of the wedge $\mathcal{N}$ should be at $\zeta = \alpha + \beta$, since that's the beginning of the ray $\mathcal{J}_{\zeta, \alpha + \beta}$. At that point, though, according to our definitions, $\mathcal{S}(\zeta)$ should consist of the point $\zeta(a) = \alpha + \beta$, and $\mathcal{S}'(\zeta)$ should consist of the point $\zeta(a') = 0$.

@@

Maybe we need to change the statement to
\[ \laplace_{\zeta,\alpha+\beta}[\phi \ast_{\zeta_\alpha, \beta} \psi] = \laplace_{\zeta,\alpha}[\phi]\,\laplace_{\zeta,\beta}[\psi]\,. \]
I think the argument might wrap up neatly in that case.
\end{todo}
\begin{align*}
\laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}] & = \int_{?} e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \int_{?} e^{z\zeta(a')}\,\psi(a')\,d\zeta(a')
\end{align*}
\end{draft}

@@

In our treatment, we will restrict the Borel transform to the space of $1$-Gevrey series and the Laplace transform to $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ with $\sigma>-1$ and $\Lambda>0$, for some domain $\Omega_\alpha$ as in Figure~\ref{fig:sectorial_domain-pos-fre}.
\begin{definition}
For $\nu \in (-\infty, 1)$, the \textit{fractional integral} $\partial^{\nu-1}_{\zeta, \alpha}$ is defined by
%
%%\[ [\partial^{\nu-1}_{\zeta, \alpha} \phi](a) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta=\alpha}^a \big(\zeta(a)-\zeta\big)^{-\nu} \phi \,d\zeta\,. \] 
\[ \partial^{\nu-1}_{\zeta, \alpha} \phi \defeq \frac{1}{\Gamma(1-\nu)} \int_{\mathcal{S}(\zeta)} \big(\zeta-\zeta(a)\big)^{-\nu} \phi(a) \,d\zeta(a)\,, \]
where $\mathcal{S}(\zeta)$ is the line segment from $\zeta(a)=\alpha$ to $\zeta(a)=\zeta$.
